### 2023-10-24 manuscript.tex
Added text and figure for Pfam overlap analysis

\section{Results}
\subsection{IDRs are shorter and more divergent than non-disordered regions}
We identified regions with high levels of inferred intrinsic disorder in over 8,500 alignments of single copy orthologs from 33 species in the \textit{Drosophila} genus using the disorder predictor AUCPreD~\cite{Wang2016}. To highlight the unique features of IDR evolution in subsequent analyses, we also extracted a complementary set of regions with low levels of inferred disorder. Both sets were filtered on several criteria, including the lengths of their sequences and their phylogenetic diversity, which yielded 11,445 and 14,927 regions, respectively, from 8,466 unique alignments. In the subsequent discussion, we refer to these sets as the ``disorder'' and ``order'' regions, respectively. To investigate the differences in basic sequence statistics between the two region sets, we first generated histograms from the average length of each region (Fig.~\ref{sfig:regions}). Although both distributions span several orders of magnitude, the order regions are generally longer than the disorder regions, with means of 105 and 245 residues, respectively. We then quantified the sequence divergence in each region by fitting phylogenetic trees to the alignments using amino acid and indel substitution models. The average rates of substitution are significantly larger in the disorder regions, demonstrating that while both sets contain conserved and divergent regions, IDRs are enriched in more rapidly evolving sequences (Fig.~\ref{sfig:regions}).

% TODO: Add sentence(s) about searching regions against Pfam domains and measuring overlap
% We also searched the database of Pfam domains against the full-length D. melanogaster proteins in these alignments and measured their overlap with the called disorder and order regions. The results show a clear enrichment in the disorder regions having no or only small amounts of overlap relative to the order regions.

>>>>

\section{Results}
\subsection{IDRs are shorter and more divergent than non-disordered regions}
We identified regions with high levels of inferred intrinsic disorder in over 8,500 alignments of single copy orthologs from 33 species in the \textit{Drosophila} genus using the disorder predictor AUCPreD~\cite{Wang2016}. To highlight the unique features of IDR evolution in subsequent analyses, we also extracted a complementary set of regions with low levels of inferred disorder. Both sets were filtered on several criteria, including the lengths of their sequences and their phylogenetic diversity, which yielded 11,445 and 14,927 regions, respectively, from 8,466 unique alignments. In the subsequent discussion, we refer to these sets as the ``disorder'' and ``order'' regions, respectively. To investigate the differences in basic sequence statistics between the two region sets, we first generated histograms from the average length of each region (Fig.~\ref{sfig:regions}). Although both distributions span several orders of magnitude, the order regions are generally longer than the disorder regions, with means of 105 and 245 residues, respectively. We then quantified the sequence divergence in each region by fitting phylogenetic trees to the alignments using amino acid and indel substitution models. The average rates of substitution are significantly larger in the disorder regions, demonstrating that while both sets contain conserved and divergent regions, IDRs are enriched in more rapidly evolving sequences (Fig.~\ref{sfig:regions}). We also searched the database of Pfam domains against the full-length \textit{D. melanogaster} proteins in these alignments and measured their overlap with the disorder and order regions. The results show a clear enrichment in the disorder regions having no or only small amounts of overlap relative to the order regions, indicating that, relative to structured domains, IDRs are especially resistant to homology-based methods of functional annotation (Fig.~\ref{sfig:pfam}).

### 2023-10-24 supporting.tex
Added TODO notes for revisions
Added text and figure for Pfam overlap analysis

\begin{figure}[h!]
\includegraphics[width=\textwidth]{regions/out/regions.png}
\centering
\caption{\textbf{Summary statistics of disorder and order regions.}
\textbf{(A)} Distribution of mean lengths of regions. \textbf{(B)} Boxplot of the sums of the average amino acid and indel substitution rates in the disorder and order regions. The substitution rates are significantly greater in the disorder regions than in the order regions ($p < 1 \times 10^{-10}$, Mann-Whitney \textit{U} test).}
\label{sfig:regions}
\end{figure}

>>>>

\begin{figure}[h!]
\includegraphics[width=\textwidth]{regions/out/regions.png}
\centering
\caption{\textbf{Summary statistics of disorder and order regions.}
\textbf{(A)} Distribution of mean lengths of regions. \textbf{(B)} Violin plot of the sums of the average amino acid and indel substitution rates in the disorder and order regions. The substitution rates are significantly greater in the disorder regions than in the order regions ($p < 1 \times 10^{-10}$, Mann-Whitney \textit{U} test).}
\label{sfig:regions}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=\textwidth]{pfam/out/pfam.png}
\centering
\caption{\textbf{Overlap of disorder and order regions with Pfam domains.}
\textbf{(A)} Number of disorder and order regions with zero and non-zero overlap with any Pfam domain. \textbf{(B)} Histogram of the disorder and order regions' overlaps with any Pfam domain. Regions with zero overlap are excluded to more clearly show the distribution.}
\label{sfig:pfam}
\end{figure}
